\textcolor{black}{Disambiguating Monocular Depth Estimation with a Single Transient: Supplemental Information}

### 2020-03-05 paper/eccv2020/sections/discussion.tex
reformat supplement, move hardware details to supplement, pass through main paper

\edit{In the optically diffused configuration, the laser
power is spread out over the entire scene. Accordingly, for distant scene points very
little light may return to the SPAD and it may be difficult to accurately
capture distant scene geometry in the histogram. Thus our method is best suited
to short to medium-range scenes with a reasonable power budget for the diffused
illumination.} \edit{For example, assuming an indoor scene with
fluorescent bulbs and an ambient spectral irradiance of $I_A =
2~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
to the laser), we find that the laser power required to achieve a minimum SBR of 5 for a
diffuse scene at $r = 2$ m
and a field of view of $\theta = 40^\circ$ can be calculated as}
%
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 r^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
\end{equation} 
\edit{giving $P_{\text{min}}=21$ mW. We note that this is significantly 
less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.}

@@

Other methods for extracting scene information from a depth histogram could be
employed, including learning-based methods to combine the MDE estimates and
histogram. One might even consider sensing regimes where the number of
returning signal photons is low, such as when the time-resolved detector and camera operate
at high framerates. While most MDE techniques are tailored to clean RGB images,  
the depth histogram could be used to help MDE
techniques generalize to noisy scenes under low-light conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Conclusions}
Since their introduction, monocular depth estimation algorithms have improved tremendously.  However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements. 
In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histogram measurements. 
Such histograms are easy to capture using time-resolved single-photon detectors and are poised to become an important component of future low-cost imaging systems.
%Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.
%Computational photography approaches may provide the measurements needed to achieve much greater performance improvements, especially as the sensors in devices we use every day become more diverse, complex, and increasingly rely on techniques based on sensor fusion and sophisticated computational algorithms.

>>>>

\edit{In the optically diffused configuration, the laser
power is spread out over the entire scene. Accordingly, for distant scene points very
little light may return to the SPAD and it may be difficult to accurately
capture distant scene geometry in the histogram. Thus our method is best suited
to short to medium-range scenes with a reasonable power budget for the diffused
illumination.} \edit{For example, assuming an indoor scene with
fluorescent bulbs and an ambient spectral irradiance of $I_A =
1~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
to the laser), we find that the laser power required to achieve a minimum SBR of 5 for a
diffuse scene at $R = 3$ m
and a field of view of $\theta = 40^\circ$ can be calculated as}
%
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 R^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
\end{equation} 
\edit{giving $P_{\text{min}}=21$ mW. We note that this is significantly 
less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.}

@@

Other methods for extracting scene information from a transient could be
employed, including learning-based methods to combine the MDE estimates and
histogram. One might even consider sensing regimes where the number of
returning signal photons is low, such as when the time-resolved detector and camera operate
at high framerates. While most MDE techniques are tailored to clean RGB images,  
the transient could be used to help MDE
techniques generalize to noisy scenes under low-light conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Conclusions}
Since their introduction, monocular depth estimation algorithms have improved tremendously.  However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements. 
In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with transient measurements. 
Such histograms are easy to capture using time-resolved single-photon detectors and are poised to become an important component of future low-cost imaging systems.
%Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.
%Computational photography approaches may provide the measurements needed to achieve much greater performance improvements, especially as the sensors in devices we use every day become more diverse, complex, and increasingly rely on techniques based on sensor fusion and sophisticated computational algorithms.

### 2020-03-05 paper/eccv2020/sections/hardware.tex
reformat supplement, move hardware details to supplement, pass through main paper

\begin{figure}[t]
	\centering
  \includegraphics[width=\columnwidth]{captured_diffuse_small.pdf}
  \caption{Captured result comparing the direct output of the MiDaS MDE and depth maps corrected by our method using the digitally aggregated transient of the scanned SPAD (center right) and a single transient captured by an optically diffused SPAD (right). Both of these approaches result in very similar results and both are significantly better than the output of the MDE, as shown by the error maps in the insets. The diffused SPAD results are captured at $\sim$25mW laser power indoors.
			%The resulting corrected depth maps from both scanning and summing transient measurements and diffusing the laser illumination are very similar qualitatively and quantitatively.
		}
  \label{fig:captured_diffuse_small}
  % \vspace{-0.5em}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
  \includegraphics[width=\columnwidth]{captured_diffuse_small.pdf}
  \caption{Captured result comparing the direct output of the MiDaS MDE and depth maps corrected by our method using the digitally aggregated transient of the scanned SPAD (center right) and a single transient captured by an optically diffused SPAD and laser (right). Both of these approaches result in very similar results and both are significantly better than the output of the MDE, as shown by the error maps in the insets. The diffused SPAD results are captured at $\sim$25mW laser power indoors.
			%The resulting corrected depth maps from both scanning and summing transient measurements and diffusing the laser illumination are very similar qualitatively and quantitatively.
		}
  \label{fig:captured_diffuse_small}
  % \vspace{-0.5em}
\end{figure}

### 2020-03-05 paper/eccv2020/supplement.tex
final pass (hopefully)
reformat supplement, move hardware details to supplement, pass through main paper

\newcommand{\edit}[1]{\textcolor{red}{#1}}

@@

%\title{Improving Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD Transient} % Replace with your title
\title{\textcolor{red}{Disambiguating Monocular Depth Estimation with a Single
    Transient: Supplemental Information}} % Replace with your title

@@

@@

\section{Nominal values for SBR calculation}
Here we give the values used in the equation for received power, repeated here
for convenience:
  \begin{equation}
    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta.
  \end{equation}
The object in question is a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
\begin{figure}[H]
  \centering
  \begin{tabular}{c|c|c}
    \toprule
    Symbol & Description & Nominal Value \\
    \midrule
    $\rho$  & Albedo of lambertian surface & $0.3$ \\
    $P_T$ & Total irradiance at wavelength (W/$\text{m}^2$) & $0.026$ \\
    $R$ & Distance to surface (m) & $3$ \\
    $A_{rec}$ & Area of detector ($\text{m}^2$) & $1.96 \times 10^{-9}$ \\
    $\eta$ & Quantum efficiency of detector & $0.3$ \\
    $P_R$ & Received power at detector (W) & $1.62 \times 10^{-13}$ \\
    \bottomrule
  \end{tabular}
  \caption{}
  \label{fig:sbr_calculation}
\end{figure}
Once $P_R$ is determined, we compute the number of photons using the laser
wavelength $\lambda = 532$ nm as
\begin{equation}
  N = \frac{P_R\lambda}{hc}
\end{equation}
where $h \approx 6.626 \tiems 10^{-34}$ is Planck's constant and $c \approx 3
\times 10^8$ is the speed of light. Now using the fact that our laser runs at 10
MHz, we get the number of photons per pulse as $0.043$, which puts us in the
low-flux regime.

In order to verify that digital summation of scanned measurements yields results
that are similar to those captured by a diffused laser and detector, we capture
an example scene using a modified hardware prototype in both scanned and
diffused modes. The hardware prototype (shown in Fig.~\ref{fig:hardware})
consists of a more powerful laser (Katana 05HP, 532 nm) which we operate at
approximately 25 mW output power with two single-pixel SPAD detectors. One SPAD
is aligned with the optical path of the laser, and the other SPAD is operated
without a lens to integrate light from the entire scene. Both SPADs are fitted
with a 10 nm bandpass filter centered at 532 nm, which reduces the amount of
integrated ambient light. We attach a holographic diffuser (Thorlabs ED1-S50) to
the laser output in order to diffuse light onto the scene or alternatively
remove the diffuser and use a pair of scanning mirrors to scan the scene.

The modified hardware setup is used to capture an example scene in both scanned and
diffused modes, and the resulting transients are used to refine an initial depth
estimate from the Kinect RGB image. We illustrate the results of this procedure
in Fig.~\ref{fig:comparison}. The reconstructions from the scanned and diffused
measurements are similar in reconstruction quality and also show similar
quantitative improvement in terms or error over the initial depth estimate. The
unnormalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
note that the counts show similar trends. The number of recorded photons in
these experiments is shown in Table~\ref{tab:photon_counts}. In both cases, the
rate of detected photons is far less ($<$5\%) than the number of emitted laser
pulses, and so we conclude that the measurements are captured in the low-flux
regime where pileup effects are negligible. We attribute most of the differences
between the scanned and diffused transients to the baseline between the
positions of the diffused and scanned SPADs (see Fig.~\ref{fig:hardware}).
\begin{figure}[H]
  \centering \includegraphics[width=\textwidth]{captured_diffuse.pdf}
  \caption{Comparing Scan + Sum and Diffused SPAD. The transients shown are
    equal-time (and thus equal energy), and display qualitative similarity in
    the absence of pileup.}
  \label{fig:comparison}
\end{figure}

\begin{figure}[H]
  \centering \includegraphics[width=\textwidth]{diffused_hardware/setup.pdf}
  \caption{Modified hardware setup. The setup is used to compare scanned and
  diffused measurements and employs two SPAD detectors and two laser
  configurations. In the first configuration, the scene is illuminated by
  sending the laser light through a holographic diffuser and a lensless SPAD 
  integrates light from the entire scene. In the second, the SPAD is aligned
  with the optical path of the laser and the scene is scanned using a pair of
  scanning mirrors. The baseline between the two SPADs (right) results in some
  observed differences in the recorded transients.}
  \label{fig:dither}
\end{figure}

\section{Additional results on NYU Depth v2}
Figures \ref{fig:densedepth_1}--\ref{fig:midas_3} show additional results
for our method on the NYU Depth v2 dataset when the depth estimate is
initialized with the DenseDepth \cite{Alhashim2018} (Figures
\ref{fig:densedepth_1}--\ref{fig:densedepth_3}), DORN \cite{Fu2018} (Figures
\ref{fig:dorn_1}--\ref{fig:dorn_3}) 
and MiDaS \cite{Lasinger:2019} (Figures \ref{fig:midas_1} -- \ref{fig:midas_3}) monocular depth estimators.

We compare the output of the network $z_0$, the
median-rescaled network output (where the depth map $z_0$ is scaled pixel-wise by a
scalar $\frac{\text{median}(z_{GT})}{\text{median}(z_0)}$, $z_{GT}$ being the
ground truth depth map), the network output matched to the ground truth depth histogram, and the output of
our histogram matching method under a signal-to-background ratio (SBR) of 100.
We use the luminance of the RGB image as our reflectance map
for both SPAD simulation and histogram matching.
We show absolute difference maps and also give
the root-mean-square error (RMSE) for each example.
\input{sections/supplement/simulation_comparison.tex}

\section{Additional results for hardware prototype}
Figures \ref{fig:midas_captured_1}--\ref{fig:dorn_captured_3} show all the
captured results when the depth estimate is initialized with the MiDaS
\cite{Lasinger:2019} (Figures \ref{fig:midas_captured_1}--\ref{fig:midas_captured_3}),
DenseDepth (Figures \ref{fig:densedepth_captured_1}--\ref{fig:densedepth_captured_3}),
and DORN (Figures \ref{fig:dorn_captured_1}--\ref{fig:dorn_captured_3}). We compare
the output of the network $z_0$, the mean-rescaled network output where the
depth map $z_0$ has been scaled pixel-wise by the scalar
$\frac{\text{median}(h_{target})}{\text{median}(z_0)}$ ($h_{target}$ is the
processed SPAD transient), and the output of our method. As our laser is red, we
use the R channel of the RGB image as our reflectance map. We show absolute
difference maps and also give the root-mean-square-error (RMSE) for each
example.

Black pixels in the ground truth depth correspond to locations where our scanner
was unable to produce an accurate depth estimate (this can occur for a variety
of reasons including dark albedo and surface specularity). These pixels are masked off and not used in the RMSE
calculation, and appear as an absolute difference of 0 in the difference maps.
 \input{sections/supplement/hardware_comparison.tex}

>>>>

\newcommand{\edit}[1]{\textcolor{black}{#1}}

@@

%\title{Improving Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD Transient} % Replace with your title
\title{\textcolor{black}{Disambiguating Monocular Depth Estimation with a Single
    Transient: Supplemental Information}} % Replace with your title

@@

\section{Hardware prototype details}
% show this in supplement
The monocular depth estimate is calculated using the RGB image captured by the Kinect v2. The SPAD records temporal histograms with 4096 bins, each corresponding to a time window of 16~ps. The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth maps with an accuracy of about 1~cm. A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene. This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth---such validation would not be possible if we were to capture measurements with an optically diffused SPAD.

% show this in supplement
%To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD, we set up a slightly modified version of our prototype consisting of both scanned and diffused SPADs side-by-side. Details about this system can be found in the supplement. We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs. The aggregated measurements from the scanned SPAD are shown alongside the optically diffused SPAD's measurements in Figure ~\ref{fig:hardware}(c). These results demonstrate that the two systems produce near equivalent measurements. Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions. That is, they observe scene from slightly different perspectives.
	%NOTE:JUSTIFY USE OF DIFFERENT PROTOTYPE FOR RESULTS IN THE WILD WITH EYE SAFETY?} \edit{We show proof-of-concept results captured by this system in   Figure~\ref{fig:captured_diffuse_small}. For}

In order to verify that digital summation of scanned measurements yields results
that are similar to those captured by a diffused laser and detector, we capture
an example scene using a modified hardware prototype in both scanned and
diffused modes. This hardware prototype (shown in Fig.~\ref{fig:hardware}) is less mobile than 
our unmodified prototype, but allows us to use a more powerful laser (Katana
05HP, 532 nm) operated at approximately 25 mW average power. We also use two
single-pixel SPAD detectors, where one SPAD is aligned with the optical path of
the laser, and the other SPAD is operated without a lens to integrate light
from the entire scene. Both SPADs are fitted with a 10 nm bandpass filter
centered at 532 nm, which reduces the amount of integrated ambient light. We
attach a holographic diffuser (Thorlabs ED1-S50) to the laser output in order
to diffuse light onto the scene. Alternatively, we remove the diffuser and use a
pair of scanning mirrors to scan the scene.

The modified hardware setup is used to capture an example scene in both scanned and
diffused modes, and the resulting transients are used to refine an initial depth
estimate from the Kinect RGB image. We illustrate the results of this procedure
in Fig.~\ref{fig:comparison}. The reconstructions from the scanned and diffused
measurements are similar in reconstruction quality and also show similar
quantitative improvement in terms of error over the initial depth estimate. The
unnormalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
note that the counts show similar trends. The number of recorded photons in
these experiments is shown in Table~\ref{tab:photon_counts}. In both cases, the
rate of detected photons is far less ($<$5\%) than the number of emitted laser
pulses, and so we conclude that the measurements are captured in the low-flux
regime where pileup effects are negligible. We attribute most of the differences
between the scanned and diffused transients to the approximately 16 cm vertical
baseline between the positions of the diffused and scanned SPADs (see
Fig.~\ref{fig:hardware}).
\begin{figure}[H]
  \centering \includegraphics[width=\textwidth]{diffused_hardware/setup.pdf}
  \caption{Modified hardware setup. The setup is used to compare scanned and
  diffused measurements and employs two SPAD detectors and two laser
  configurations. In the first configuration, the scene is illuminated by
  sending the laser light through a holographic diffuser and a lensless SPAD 
  integrates light from the entire scene. In the second, the SPAD is aligned
  with the optical path of the laser and the scene is scanned using a pair of
  scanning mirrors. The baseline between the two SPADs (right) results in some
  observed differences in the recorded transients.}
  \label{fig:hardware}
\end{figure}

\begin{figure}[H]
  \centering \includegraphics[width=\textwidth]{captured_diffuse.pdf}
  \caption{Comparison of scan + sum and diffused SPAD. The transients are captured
      with the same total exposure time and are qualitatively similar without 
      noticeable pileup effects.}
  \label{fig:comparison}
\end{figure}

\section{Nominal values for SBR calculation}
Here we give the values used in the equation for received power, repeated here
for convenience:
  \begin{equation}
    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta.
  \end{equation}
The object in question is a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
\begin{figure}[H]
  \centering
  \begin{tabular}{c|c|c}
    \toprule
    Symbol & Description & Nominal Value \\
    \midrule
    $\rho$  & Albedo of lambertian surface & $0.3$ \\
    $P_T$ & Total irradiance at wavelength (W/$\text{m}^2$) & $0.026$ \\
    $R$ & Distance to surface (m) & $3$ \\
    $A_{rec}$ & Area of detector ($\text{m}^2$) & $1.96 \times 10^{-9}$ \\
    $\eta$ & Quantum efficiency of detector & $0.3$ \\
    $P_R$ & Received power at detector (W) & $1.62 \times 10^{-13}$ \\
    \bottomrule
  \end{tabular}
  \caption{}
  \label{fig:sbr_calculation}
\end{figure}
Once $P_R$ is determined, we compute the number of photons using the laser
wavelength $\lambda = 532$ nm as
\begin{equation}
  N = \frac{P_R\lambda}{hc}
\end{equation}
where $h \approx 6.626 \times 10^{-34}$ is Planck's constant and $c \approx 3
\times 10^8$ is the speed of light. Now using the fact that our laser runs at 10
MHz, we get the number of photons per pulse as $0.043$, which puts us in the
low-flux regime.

@@

\clearpage
\section{Additional results on NYU Depth v2}
Figures \ref{fig:densedepth_1}--\ref{fig:midas_3} show additional results
for our method on the NYU Depth v2 dataset when the depth estimate is
initialized with the DenseDepth \cite{Alhashim2018} (Figures
\ref{fig:densedepth_1}--\ref{fig:densedepth_3}), DORN \cite{Fu2018} (Figures
\ref{fig:dorn_1}--\ref{fig:dorn_3}) 
and MiDaS \cite{Lasinger:2019} (Figures \ref{fig:midas_1} -- \ref{fig:midas_3}) monocular depth estimators.

We compare the output of the network $z_0$, the
median-rescaled network output (where the depth map $z_0$ is scaled pixel-wise by a
scalar $\frac{\text{median}(z_{GT})}{\text{median}(z_0)}$, $z_{GT}$ being the
ground truth depth map), the network output matched to the ground truth depth histogram, and the output of
our histogram matching method under a signal-to-background ratio (SBR) of 100.
We use the luminance of the RGB image as our reflectance map
for both SPAD simulation and histogram matching.
We show absolute difference maps and also give
the root-mean-square error (RMSE) for each example.

\newpage
\input{sections/supplement/simulation_comparison.tex}

\clearpage
\section{Additional results for hardware prototype}
Figures \ref{fig:midas_captured_1}--\ref{fig:dorn_captured_3} show all the
captured results when the depth estimate is initialized with the MiDaS
\cite{Lasinger:2019} (Figures \ref{fig:midas_captured_1}--\ref{fig:midas_captured_3}),
DenseDepth (Figures \ref{fig:densedepth_captured_1}--\ref{fig:densedepth_captured_3}),
and DORN (Figures \ref{fig:dorn_captured_1}--\ref{fig:dorn_captured_3}). We compare
the output of the network $z_0$, the mean-rescaled network output where the
depth map $z_0$ has been scaled pixel-wise by the scalar
$\frac{\text{median}(h_{target})}{\text{median}(z_0)}$ ($h_{target}$ is the
processed SPAD transient), and the output of our method. As our laser is red, we
use the R channel of the RGB image as our reflectance map. We show absolute
difference maps and also give the root-mean-square-error (RMSE) for each
example.

Black pixels in the ground truth depth correspond to locations where our scanner
was unable to produce an accurate depth estimate (this can occur for a variety
of reasons including dark albedo and surface specularity). These pixels are masked off and not used in the RMSE
calculation, and appear as an absolute difference of 0 in the difference maps.

\newpage

\input{sections/supplement/hardware_comparison.tex}
